### 2021-02-18 preliminaries.tex
defined ReLU/sigmoid

A \emph{feed-forward neural network} is a directed acyclic graph
of differentiable \emph{modules} that operate on numeric vectors.
The common modules include multiplication by a matrix, and nonlinearity such as ReLU or sigmoid.
Some of the modules are parameterized by trainable parameters or hyperparameters.
In a typical usage, the neural network is trained by \emph{gradient descent}.
In this setting, the trained network outputs a single numeric value called \emph{loss}.
Since the network is differentiable,
a gradient of the loss is computed with respect to all the trainable parameters of the network.
The gradients are typically computed by \emph{backpropagation}.
The values of the parameters are then updated by taking a small step in the direction that minimizes the loss.

\todo{Define sigmoid.}
\todo{Maybe we don't need to make GCN a preliminary; we can define it later instead.}
\todo[inline,author=FB]{GCN? Backprop?, gradient descent, loss, gradient, epoch}

>>>>

A \emph{feed-forward neural network} is a directed acyclic graph
of differentiable \emph{modules} that operate on numeric vectors.
The common modules include multiplication by a matrix, and nonlinearity such as ReLU or sigmoid.\footnote{
These are, respectively, $f(x) = \max\{0,x\}$ and $g(x) = 1/(1+e^{-x}$). }
Some of the modules are parameterized by trainable parameters or hyperparameters.
In a typical usage, the neural network is trained by \emph{gradient descent}.
In this setting, the trained network outputs a single numeric value called \emph{loss}.
Since the network is differentiable,
a gradient of the loss is computed with respect to all the trainable parameters of the network.
The gradients are typically computed by \emph{backpropagation}.
The values of the parameters are then updated by taking a small step in the direction that minimizes the loss.

\todo{Maybe we don't need to make GCN a preliminary; we can define it later instead.}
\todo[inline,author=FB]{GCN? Backprop?, gradient descent, loss, gradient, epoch}
